### 2023-04-19 introduction.tex
details
section 2

MFCS 2023 \\
Abstract submission deadline:    	April 24th (AoE) \\
Paper submission deadline:    	April 28th (AoE)

>>>>

{\bf MFCS 2023
Abstract submission deadline:    	 April 24th (AoE) 
Paper submission deadline:    	April 28th (AoE)} \\
%
{\bf CONCUR 2023 Abstract Registration Due 	Apr 24, 2023
Submission Deadline 	May 2, 2023}\\
%
{\bf FSTTCS 2033  Submission deadline: July 14, 2022 AoE (firm)
Notification to authors: September 16, 2022}

trop d'hypotheses trop fortes sur les WSTS

{\bf Our contributions}
We introduce a more general definition of resilience generalising the two given in \cite{DBLP:conf/gg/Ozkan22}.
Surprinsingly, the general undecidability statements were not known neither proved.
